Applying LIME to Bullet Data Journal

### 2018-12-19 journal/applying LIME to bullet data journal.Rmd
updated journal after meeting and made two versions of app

# December 5, 2018 to December 14, 2018

@@

## Previous Work

### Feature Plots of Training and Testing Data Filled by `samesource`

@@

### Correlation Plots of Training and Testing Data

@@

### Visualizations of the LIME Explanations

@@

### Draft of LIME Procedure from the `lime` R Package

@@

## Work on Determining Input Values for LIME

@@

### Assessing the Accuracy of the LIME Results

@@

#### Complex versus Simple Model Predictions

@@

#### Comparing Input Values by MSE and $R^2$

@@

### Assessing the Variability of the LIME Results

@@

@@

### Deciding on LIME Input Settings

@@

```{r}
library(rpart)

tree <- rpart(samesource ~ ccf, data = hamby173and252_train, 
              control = rpart.control(cp = 0.0005, maxdepth = 2))
plot(tree)
text(tree)

tree2 <- cutree(tree, k = 5)
```

>>>>

## December 5, 2018 to December 14, 2018

@@

### Previous Work

#### Feature Plots of Training and Testing Data Filled by `samesource`

@@

#### Correlation Plots of Training and Testing Data

@@

#### Visualizations of the LIME Explanations

@@

#### Draft of LIME Procedure from the `lime` R Package

@@

### Work on Determining Input Values for LIME

@@

#### Assessing the Accuracy of the LIME Results

@@

##### Complex versus Simple Model Predictions

@@

##### Comparing Input Values by MSE and $R^2$

@@

#### Assessing the Variability of the LIME Results

@@

In the meeting with Heike, we talked about how this plot suggests that LIME is not doing a very good job of providing local explanations. Regardless of the case, it is often suggesting only one of two variables are important, and the variable importance depends on the number of bins. In this plot, I would like consistency in the x-direction, but I would like variability in the y-direction to better understand the variables that are important for a specific case.

@@

#### Deciding on LIME Input Settings

@@

#### Notes on meeting with Heike

* We talked about including the penalty for the number of parameters in the dicussion of the paper.
* We talked about using a tree to choose the bins. This would allow us to automate the process and to obtain a penalty parameter since the trees give us nesting. (MSE + lambda * p where p is the from the number of trees multiplied by the number of ...)
* Look at the AUC after binning

## December 15, 2018 to January 8, 2018

Heike wrote the function `treebink` to take x and y variables for fitting a tree and returning the cuts for $k$ bins based on the splits from the tree. Here is an example using the function below with the predictor variable of ccf.

```{r echo = TRUE}
treebink(y = hamby173and252_train$samesource, x = hamby173and252_train$ccf, k = 5)
```
